A Domain Specific Language for SpectreGuard

### 2020-12-07 paper/main.tex
Clarify generated code slightly
Add more horizontal lines to naming table
wibble

\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    EDSL name in \ttt{example5} & Generated C Name \\
    \hline
    \verb|secretArray| & \verb|_fs_0|\\
    \verb|publicArray| & \verb|_fs_1|\\
    \verb|leak| & \verb|_fs_3|\\
    \verb|secretArrayA| & \verb|_fs_5|\\
    \verb|secretArrayB| & \verb|_fs_6|\\
    \verb|publicArray2| & \verb|_fs_7|\\
    \verb|leak2| & \verb|_fs_9|\\
    \hline
  \end{tabular}
\caption{Correspondence between EDSL names and generated C names for \ttt{example5}}
\label{table:Names5}
\end{table}

@@

\section{Future Work}
A further investigation into the tradeoffs and possible additional features of
the information flow analysis is likely to be useful. This could provide a more
accurate and succinct picture to programmers of where leaks are occurring, or
potentially occurring. It is possible that some of these other leak conditions
could be incorporated into the type system, by exploiting the dependent type
features enabled by singletons~\cite{SingletonsPaper} and, in the future, by Dependent Haskell.~\cite{DepHaskSpec}
Dependent types provide a powerful technique for writing programs at a type-level, which
will be executed at compile-time by the type checker.~\cite{CertProg}

>>>>

\begin{table}
  \centering
  \begin{tabular}{|c|c|}
    \hline
    EDSL name in \ttt{example5} & Generated C Name \\
    \hline
    \verb|secretArray| & \verb|_fs_0|\\
    \hline
    \verb|publicArray| & \verb|_fs_1|\\
    \hline
    \verb|leak| & \verb|_fs_3|\\
    \hline
    \verb|secretArrayA| & \verb|_fs_5|\\
    \hline
    \verb|secretArrayB| & \verb|_fs_6|\\
    \hline
    \verb|publicArray2| & \verb|_fs_7|\\
    \hline
    \verb|leak2| & \verb|_fs_9|\\
    \hline
  \end{tabular}
\caption{Correspondence between EDSL names and generated C names for \ttt{example5}}
\label{table:Names5}
\end{table}

@@

\section{Related Work}
...

\section{Future Work}
A further investigation into the tradeoffs and possible additional features of
the information flow analysis is likely to be useful. This could provide a more
accurate and succinct picture to programmers of where leaks are occurring, or
potentially occurring. It is possible that some of these other leak conditions
could be incorporated into the type system, by exploiting the dependent type
features enabled by singletons~\cite{SingletonsPaper} and, in the future, by Dependent Haskell.~\cite{DepHaskSpec}
Dependent types provide a powerful technique for writing programs at a type-level, which
will be executed at compile-time by the type checker.~\cite{CertProg, DepHaskSpec}
